---
title: "sanzo"
author: "Jacqueline Maasch"
date: "12/17/2019"
output: html_document
---

```{r data, echo = FALSE, message = FALSE, warning = FALSE}

# Use in-built datasets for base R demos.
data("iris")
data("BOD")
data("faithfuld")
data("DNase")

# Load packages for ggplot2 demos.
library(ggplot2)
library(ggthemes)
library(cowplot)

# Read in data for ggplot2 demos.
raw <- read.csv("/Users/razel/Desktop/PROGS/R_practice/2019/sth_plasmid_ct_mean_raw.csv")
mean <- read.csv("/Users/razel/Desktop/PROGS/R_practice/2019/sth_plasmid_ct_mean.csv")
ct <- read.csv("/Users/razel/Desktop/PROGS/R_practice/2019/niger_giardia_swab_study_2019/niger_comparative_ct_by_duplicate.csv")

```

## Palette definitions.

Duos, trios, and quads stored in lists.

```{r palettes, echo = FALSE}

duos <- list(
  c006 = c("#ff616b", "#000831"),
  c007 = c("#ff5200", "#b3e8c2"),
  c008 = c("#c2612c", "#b8b8ff"),
  c033 = c("#b85e00", "#1b3644"),
  c035 = c("#b08699", "#a10b2b"),
  c047 = c("#c9303e", "#bfabcc"),
  c070 = c("#b85e00", "#405416"),
  c071 = c("#a90636", "#d99e73"),
  c074 = c("#b5ffc2", "#2dbc94"),
  c079 = c("#651300", "#2dbc94"),
  c085 = c("#c74300", "#008aa1"),
  c091 = c("#5c2c45", "#c05200"),
  c095 = c("#681916", "#06004f"),
  c102 = c("#ebd999", "#c05200"),
  c103 = c("#c2612c", "#2d0060"),
  c106 = c("#008aa1", "#06004f"),
  c114 = c("#ffab00", "#008aa1"),
  c118 = c("#e0b81f", "#362304"),
  c119 = c("#a6e6db", "#0d2b52"),
  c229 = c("#172713", "#b5d1cc")
)

trios <- list(
  c121 = c("#6c2b11", "#d99e73", "#405416"),
  c139 = c("#96bfe6", "#000831", "#b5d1cc"),
  c142 = c("#9e194d", "#baa600", "#96bfe6"),
  c148 = c("#d1bd19", "#ffab00", "#29bdad"),
  c149 = c("#d1bd19", "#ff5200", "#0f261f"),
  c157 = c("#6f0043", "#d1bd19", "#4f8fe6"),
  c163 = c("#ffe600", "#b5ffc2", "#008aa1"),
  c171 = c("#730f1f", "#ff8c00", "#b3e8c2"),
  c172 = c("#c2612c", "#008aa1", "#3400a3"),
  c174 = c("#ffa6d9", "#bfabcc", "#6b2e63"),
  c194 = c("#fa2b00", "#ffcfc4", "#4f8fe6"),
  c204 = c("#b319ab", "#c2612c", "#a6e6db"),
  c205 = c("#730f1f", "#f59994", "#2619d1"),
  c207 = c("#9b5348", "#b3e8c2", "#000000"),
  c223 = c("#b08699", "#d99e73", "#b5ffc2"),
  c226 = c("#5c2c45", "#ffb852", "#2619d1"),
  c232 = c("#d60036", "#f2ad78", "#000831"),
  c239 = c("#b08699", "#c4bf33", "#b3e8c2"),
  c240 = c("#ff788c", "#ffff00", "#29bdad"),
  c343 = c("#a93400", "#ebd999", "#505423")
)

quads <- list(
  c249 = c("#681916", "#c0b490", "#d1bd19", "#417777"),
  c252 = c("#e62e73", "#b85e00", "#baa600", "#2dbc94"),
  c263 = c("#a93400", "#f2ad78", "#b5ffc2", "#1b3644"),
  c268 = c("#b08699", "#b85e00", "#172713", "#bfffe6"),
  c271 = c("#b90078", "#94ff94", "#2dbc94", "#0f261f"),
  c273 = c("#ffb3f0", "#6f0043", "#9b5348", "#b5d1cc"),
  c279 = c("#b85e00", "#f59994", "#c0b490", "#0d2b52"),
  c283 = c("#a7374b", "#730f1f", "#85b857", "#6bffb3"),
  c289 = c("#f2ff26", "#bdf226", "#202d85", "#06004f"),
  c293 = c("#b85e00", "#b5ffc2", "#65a98f", "#40c945"),
  c296 = c("#f5f5b8", "#d99e73", "#5e4017", "#1b3644"),
  c302 = c("#ffb852", "#c0b490", "#bfffe6", "#008aa1"),
  c310 = c("#f5f5b8", "#f2ad78", "#718600", "#172713"),
  c321 = c("#b08699", "#f5f5b8", "#172713", "#96bfe6"),
  c329 = c("#ffb852", "#bfabcc", "#340059", "#1b3644"),
  c330 = c("#bcd382", "#bfffe6", "#96bfe6", "#2dbc94"),
  c332 = c("#ff7399", "#d50c42", "#172713", "#00592e"),
  c339 = c("#d99e73", "#de4500", "#a6e6db", "#202d85"),
  c341 = c("#ff616b", "#328e13", "#172713", "#a6e6db"),
  c348 = c("#bcd382", "#328e13", "#172713", "#340059")
)

```

# Functions.
* ```sanzo.duo()``` : create duo palette
* ```sanzo.trio()``` : create trio palette
* ```sanzo.quad()``` : create quad palette
* ```sanzo.demo2()``` : print demo plots for all duo palettes
* ```sanzo.demo3()``` : print demo plots for all trio palettes
* ```sanzo.demo4()``` : print demo plots for all quad palettes
* ```sanzo.demo.all()``` : print demo plots for all palettes
* ```sanzo.info2()``` : generate dataframe of hexadecimals and urls for all duo palettes
* ```sanzo.info3()``` : generate dataframe of hexadecimals and urls for all trio palettes
* ```sanzo.info4()``` : generate dataframe of hexadecimals and urls for all quad palettes
* ```sanzo.info.all()``` : generate dataframe of hexadecimals and urls for all palettes

```{r functions, echo = FALSE}

# Generate two-toned palette from sanzoDuos.
sanzo2 <- function(paletteName) {
  palette <- duos[[paletteName]]
}

# Generate three-toned palette from sanzoTrios.
sanzo3 <- function(paletteName) {
  palette <- trios[[paletteName]]
}

# Generate four-toned palette from sanzoQuads.
sanzo4 <- function(paletteName) {
  palette <- quads[[paletteName]]
}

# Print plots using color palette as a demo.
# @param palette = palette name
# @param n = number of colors in the palette
demo2 <- function() {

  layout(matrix(1:4, nrow = 2))
  par(mar = c(2, 2, 2, 2))
  
  barplot(BOD$demand, col = sanzo2("c006"), main = "Combination 006", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Sepal.Length, pch = 18:19, 
       col = sanzo2("c006") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#ff616b", "#000831"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo2("c006"), pch = 15, bty = "n")
  
  barplot(BOD$demand, col = sanzo2("c007"), main = "Combination 007", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Sepal.Length, pch = 18:19, 
       col = sanzo2("c007") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#ff5200", "#b3e8c2"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo2("c007"), pch = 15, bty = "n")
  
  barplot(BOD$demand, col = sanzo2("c008"), main = "Combination 008", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Sepal.Length, pch = 18:19, 
       col = sanzo2("c008") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#c2612c", "#b8b8ff"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo2("c008"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo2("c033"), main = "Combination 033", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Sepal.Length, pch = 18:19, 
       col = sanzo2("c033") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#b85e00", "#1b3644"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo2("c033"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo2("c035"), main = "Combination 035", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Sepal.Length, pch = 18:19, 
       col = sanzo2("c035") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#b08699", "#a10b2b"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo2("c035"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo2("c047"), main = "Combination 047", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Sepal.Length, pch = 18:19, 
       col = sanzo2("c047") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#c9303e", "#bfabcc"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo2("c047"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo2("c070"), main = "Combination 070", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Sepal.Length, pch = 18:19, 
       col = sanzo2("c070") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#b85e00", "#405416"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo2("c070"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo2("c071"), main = "Combination 071", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Sepal.Length, pch = 18:19, 
       col = sanzo2("c071") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#a90636", "#d99e73"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo2("c071"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo2("c074"), main = "Combination 074", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Sepal.Length, pch = 18:19, 
       col = sanzo2("c074") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#b5ffc2", "#2dbc94"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo2("c074"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo2("c079"), main = "Combination 079", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Sepal.Length, pch = 18:19, 
       col = sanzo2("c079") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#651300", "#2dbc94"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo2("c079"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo2("c085"), main = "Combination 085", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Sepal.Length, pch = 18:19, 
       col = sanzo2("c085") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#c74300", "#008aa1"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo2("c085"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo2("c091"), main = "Combination 091", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Sepal.Length, pch = 18:19, 
       col = sanzo2("c091") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#5c2c45", "#c05200"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo2("c091"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo2("c095"), main = "Combination 095", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Sepal.Length, pch = 18:19, 
       col = sanzo2("c095") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#681916", "#06004f"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo2("c095"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo2("c102"), main = "Combination 102", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Sepal.Length, pch = 18:19, 
       col = sanzo2("c102") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#ebd999", "#c05200"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo2("c102"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo2("c103"), main = "Combination 103", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Sepal.Length, pch = 18:19, 
       col = sanzo2("c103") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#c2612c", "#2d0060"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo2("c103"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo2("c106"), main = "Combination 106", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Sepal.Length, pch = 18:19, 
       col = sanzo2("c106") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#008aa1", "#06004f"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo2("c106"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo2("c114"), main = "Combination 114", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Sepal.Length, pch = 18:19, 
       col = sanzo2("c114") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#ffab00", "#008aa1"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo2("c114"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo2("c118"), main = "Combination 118", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Sepal.Length, pch = 18:19, 
       col = sanzo2("c118") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#e0b81f", "#362304"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo2("c118"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo2("c119"), main = "Combination 119", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Sepal.Length, pch = 18:19, 
       col = sanzo2("c119") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#a6e6db", "#0d2b52"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo2("c119"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo2("c229"), main = "Combination 229", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Sepal.Length, pch = 18:19, 
       col = sanzo2("c229") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#172713", "#b5d1cc"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo2("c229"), pch = 15, bty = "n")

}

# Print plots using color palette as a demo.
# @param palette = palette name
# @param n = number of colors in the palette
demo3 <- function() {
  
  layout(matrix(1:4, nrow = 2))
  par(mar = c(2, 2, 2, 2))
  
  barplot(BOD$demand, col = sanzo3("c121"), main = "Combination 121", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Petal.Width, pch = 18:20, 
       col = sanzo3("c121") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#6c2b11", "#d99e73", "#405416"),horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo3("c121"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo3("c139"), main = "Combination 139", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Petal.Width, pch = 18:20, 
       col = sanzo3("c139") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#96bfe6", "#000831", "#b5d1cc"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo3("c139"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo3("c142"), main = "Combination 142", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Petal.Width, pch = 18:20, 
       col = sanzo3("c142") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#9e194d", "#baa600", "#96bfe6"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo3("c142"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo3("c148"), main = "Combination 148", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Petal.Width, pch = 18:20, 
       col = sanzo3("c148") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#d1bd19", "#ffab00", "#29bdad"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo3("c148"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo3("c149"), main = "Combination 149", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Petal.Width, pch = 18:20, 
       col = sanzo3("c149") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#d1bd19", "#ff5200", "#0f261f"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo3("c149"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo3("c157"), main = "Combination 157", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Petal.Width, pch = 18:20, 
       col = sanzo3("c157") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#6f0043", "#d1bd19", "#4f8fe6"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo3("c157"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo3("c163"), main = "Combination 163", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Petal.Width, pch = 18:20, 
       col = sanzo3("c163") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#ffe600", "#b5ffc2", "#008aa1"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo3("c163"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo3("c171"), main = "Combination 171", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Petal.Width, pch = 18:20, 
       col = sanzo3("c171") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#730f1f", "#ff8c00", "#b3e8c2"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo3("c171"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo3("c172"), main = "Combination 172", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Petal.Width, pch = 18:20, 
       col = sanzo3("c172") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#c2612c", "#008aa1", "#3400a3"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo3("c172"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo3("c174"), main = "Combination 174", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Petal.Width, pch = 18:20, 
       col = sanzo3("c174") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#ffa6d9", "#bfabcc", "#6b2e63"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo3("c174"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo3("c194"), main = "Combination 194", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Petal.Width, pch = 18:20, 
       col = sanzo3("c194") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#fa2b00", "#ffcfc4", "#4f8fe6"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo3("c194"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo3("c204"), main = "Combination 204", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Petal.Width, pch = 18:20, 
       col = sanzo3("c204") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#b319ab", "#c2612c", "#a6e6db"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo3("c204"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo3("c205"), main = "Combination 205", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Petal.Width, pch = 18:20, 
       col = sanzo3("c205") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#730f1f", "#f59994", "#2619d1"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo3("c205"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo3("c207"), main = "Combination 207", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Petal.Width, pch = 18:20, 
       col = sanzo3("c207") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#9b5348", "#b3e8c2", "#000000"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo3("c207"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo3("c223"), main = "Combination 223", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Petal.Width, pch = 18:20, 
       col = sanzo3("c223") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#b08699", "#d99e73", "#b5ffc2"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo3("c223"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo3("c226"), main = "Combination 226", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Petal.Width, pch = 18:20, 
       col = sanzo3("c226") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#5c2c45", "#ffb852", "#2619d1"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo3("c226"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo3("c232"), main = "Combination 232", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Petal.Width, pch = 18:20, 
       col = sanzo3("c232") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#d60036", "#f2ad78", "#000831"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo3("c232"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo3("c239"), main = "Combination 239", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Petal.Width, pch = 18:20, 
       col = sanzo3("c239") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#b08699", "#c4bf33", "#b3e8c2"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo3("c239"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo3("c240"), main = "Combination 240", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Petal.Width, pch = 18:20, 
       col = sanzo3("c240") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#ff788c", "#ffff00", "#29bdad"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo3("c240"), pch = 15, bty = "n")

  barplot(BOD$demand, col = sanzo3("c343"), main = "Combination 343", 
          ylim = c(0, 20), border = NA)
  plot(iris$Sepal.Width, iris$Petal.Width, pch = 18:20, 
       col = sanzo3("c343") [unclass(iris$Species)], ann = FALSE)
  legend("top", legend = c("#a93400", "#ebd999", "#505423"), horiz = TRUE, xpd = TRUE, 
         inset = c(-0.24), col = sanzo3("c343"), pch = 15, bty = "n")

  }

# Print plots using color palette as a demo.
# @param palette = palette name
# @param n = number of colors in the palette
demo4 <- function() {
  
  x <- c(1, 2, 3, 4, 5, 6, 7, 8)
  y <- c(6.5, 9.6, 8.9, 12.1, 13.2, 16.9, 15.8, 19)
  
  df_bar <- data.frame(x, y)
  
  group1 <- rnorm(40, mean = 80.2, sd = 9.7)
  group2 <- rnorm(20, mean = 75.3, sd = 15)
  group3 <- rnorm(30, mean = 43.3, sd = 10.2)
  group4 <- rnorm(20, mean = 55.8, sd = 12)
  value <- c(group1, group2, group3, group4)
  category <- c(1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 
                1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1,
                2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 
                3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3,
                3, 3, 3, 3, 3, 3, 3, 3, 3, 3,
                4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4)
  
  df_scatter <- data.frame(value, category)
  
  layout(matrix(1:4, nrow = 2))
  par(mar = c(2, 2, 2, 2))
  
  barplot(df_bar$y, col = sanzo4("c249"), main = "Combination 249", 
          ylim = c(0, 20), border = NA)
  plot(df_scatter$value, pch = 18:20, 
       col = sanzo4("c249") [unclass(df_scatter$category)], ann = FALSE)
  legend("top", legend = c("#681916", "#c0b490", "#d1bd19", "#417777"), horiz = TRUE, 
         xpd = TRUE, inset = c(-0.24), col = sanzo4("c249"), pch = 15, bty = "n")

  barplot(df_bar$y, col = sanzo4("c252"), main = "Combination 252", 
          ylim = c(0, 20), border = NA)
  plot(df_scatter$value, pch = 18:20, 
       col = sanzo4("c252") [unclass(df_scatter$category)], ann = FALSE)
  legend("top", legend = c("#e62e73", "#b85e00", "#baa600", "#2dbc94"), horiz = TRUE, 
         xpd = TRUE, inset = c(-0.24), col = sanzo4("c252"), pch = 15, bty = "n")

  barplot(df_bar$y, col = sanzo4("c263"), main = "Combination 263", 
          ylim = c(0, 20), border = NA)
  plot(df_scatter$value, pch = 18:20, 
       col = sanzo4("c263") [unclass(df_scatter$category)], ann = FALSE)
  legend("top", legend = c("#a93400", "#f2ad78", "#b5ffc2", "#1b3644"), horiz = TRUE, 
         xpd = TRUE, inset = c(-0.24), col = sanzo4("c263"), pch = 15, bty = "n")

  barplot(df_bar$y, col = sanzo4("c268"), main = "Combination 268",
          ylim = c(0, 20), border = NA)
  plot(df_scatter$value, pch = 18:20, 
       col = sanzo4("c268") [unclass(df_scatter$category)], ann = FALSE)
  legend("top", legend = c("#b08699", "#b85e00", "#172713", "#bfffe6"), horiz = TRUE, 
         xpd = TRUE, inset = c(-0.24), col = sanzo4("c268"), pch = 15, bty = "n")

  barplot(df_bar$y, col = sanzo4("c271"), main = "Combination 271", 
          ylim = c(0, 20), border = NA)
  plot(df_scatter$value, pch = 18:20, 
       col = sanzo4("c271") [unclass(df_scatter$category)], ann = FALSE)
  legend("top", legend = c("#b90078", "#94ff94", "#2dbc94", "#0f261f"), horiz = TRUE, 
         xpd = TRUE, inset = c(-0.24), col = sanzo4("c271"), pch = 15, bty = "n")

  barplot(df_bar$y, col = sanzo4("c273"), main = "Combination 273", 
          ylim = c(0, 20), border = NA)
  plot(df_scatter$value, pch = 18:20, 
       col = sanzo4("c273") [unclass(df_scatter$category)], ann = FALSE)
  legend("top", legend = c("#ffb3f0", "#6f0043", "#9b5348", "#b5d1cc"), horiz = TRUE, 
         xpd = TRUE, inset = c(-0.24), col = sanzo4("c273"), pch = 15, bty = "n")
  
  barplot(df_bar$y, col = sanzo4("c279"), main = "Combination 279", 
          ylim = c(0, 20), border = NA)
  plot(df_scatter$value, pch = 18:20, 
       col = sanzo4("c279") [unclass(df_scatter$category)], ann = FALSE)
  legend("top", legend = c("#b85e00", "#f59994", "#c0b490", "#0d2b52"), horiz = TRUE, 
         xpd = TRUE, inset = c(-0.24), col = sanzo4("c279"), pch = 15, bty = "n")

  barplot(df_bar$y, col = sanzo4("c283"), main = "Combination 283", 
          ylim = c(0, 20), border = NA)
  plot(df_scatter$value, pch = 18:20, 
       col = sanzo4("c283") [unclass(df_scatter$category)], ann = FALSE)
  legend("top", legend = c("#a7374b", "#730f1f", "#85b857", "#6bffb3"), horiz = TRUE, 
         xpd = TRUE, inset = c(-0.24), col = sanzo4("c283"), pch = 15, bty = "n")

  barplot(df_bar$y, col = sanzo4("c289"), main = "Combination 289", 
          ylim = c(0, 20), border = NA)
  plot(df_scatter$value, pch = 18:20, 
       col = sanzo4("c289") [unclass(df_scatter$category)], ann = FALSE)
  legend("top", legend = c("#f2ff26", "#bdf226", "#202d85", "#06004f"), horiz = TRUE, 
         xpd = TRUE, inset = c(-0.24), col = sanzo4("c289"), pch = 15, bty = "n")

  barplot(df_bar$y, col = sanzo4("c293"), main = "Combination 293", 
          ylim = c(0, 20), border = NA)
  plot(df_scatter$value, pch = 18:20, 
       col = sanzo4("c293") [unclass(df_scatter$category)], ann = FALSE)
  legend("top", legend = c("#b85e00", "#b5ffc2", "#65a98f", "#40c945"), horiz = TRUE, 
         xpd = TRUE, inset = c(-0.24), col = sanzo4("c293"), pch = 15, bty = "n")

  barplot(df_bar$y, col = sanzo4("c296"), main = "Combination 296", 
          ylim = c(0, 20), border = NA)
  plot(df_scatter$value, pch = 18:20, 
       col = sanzo4("c296") [unclass(df_scatter$category)], ann = FALSE)
  legend("top", legend = c("#f5f5b8", "#d99e73", "#5e4017", "#1b3644"), horiz = TRUE, 
         xpd = TRUE, inset = c(-0.24), col = sanzo4("c296"), pch = 15, bty = "n")

  barplot(df_bar$y, col = sanzo4("c302"), main = "Combination 302", 
          ylim = c(0, 20), border = NA)
  plot(df_scatter$value, pch = 18:20, 
       col = sanzo4("c302") [unclass(df_scatter$category)], ann = FALSE)
  legend("top", legend = c("#ffb852", "#c0b490", "#bfffe6", "#008aa1"), horiz = TRUE, 
         xpd = TRUE, inset = c(-0.24), col = sanzo4("c302"), pch = 15, bty = "n")

  barplot(df_bar$y, col = sanzo4("c310"), main = "Combination 310", 
          ylim = c(0, 20), border = NA)
  plot(df_scatter$value, pch = 18:20, 
       col = sanzo4("c310") [unclass(df_scatter$category)], ann = FALSE)
  legend("top", legend = c("#f5f5b8", "#f2ad78", "#718600", "#172713"), horiz = TRUE, 
         xpd = TRUE, inset = c(-0.24), col = sanzo4("c310"), pch = 15, bty = "n")

  barplot(df_bar$y, col = sanzo4("c321"), main = "Combination 321", 
          ylim = c(0, 20), border = NA)
  plot(df_scatter$value, pch = 18:20, 
       col = sanzo4("c321") [unclass(df_scatter$category)], ann = FALSE)
  legend("top", legend = c("#b08699", "#f5f5b8", "#172713", "#96bfe6"), horiz = TRUE, 
         xpd = TRUE, inset = c(-0.24), col = sanzo4("c321"), pch = 15, bty = "n")

  barplot(df_bar$y, col = sanzo4("c329"), main = "Combination 329", 
          ylim = c(0, 20), border = NA)
  plot(df_scatter$value, pch = 18:20, 
       col = sanzo4("c329") [unclass(df_scatter$category)], ann = FALSE)
  legend("top", legend = c("#ffb852", "#bfabcc", "#340059", "#1b3644"), horiz = TRUE, 
         xpd = TRUE, inset = c(-0.24), col = sanzo4("c329"), pch = 15, bty = "n")

  barplot(df_bar$y, col = sanzo4("c330"), main = "Combination 330", 
          ylim = c(0, 20), border = NA)
  plot(df_scatter$value, pch = 18:20, 
       col = sanzo4("c330") [unclass(df_scatter$category)], ann = FALSE)
  legend("top", legend = c("#bcd382", "#bfffe6", "#96bfe6", "#2dbc94"), horiz = TRUE, 
         xpd = TRUE, inset = c(-0.24), col = sanzo4("c330"), pch = 15, bty = "n")

  barplot(df_bar$y, col = sanzo4("c332"), main = "Combination 332", 
          ylim = c(0, 20), border = NA)
  plot(df_scatter$value, pch = 18:20, 
       col = sanzo4("c332") [unclass(df_scatter$category)], ann = FALSE)
  legend("top", legend = c("#ff7399", "#d50c42", "#172713", "#00592e"), horiz = TRUE, 
         xpd = TRUE, inset = c(-0.24), col = sanzo4("c332"), pch = 15, bty = "n")

  barplot(df_bar$y, col = sanzo4("c339"), main = "Combination 339", 
          ylim = c(0, 20), border = NA)
  plot(df_scatter$value, pch = 18:20, 
       col = sanzo4("c339") [unclass(df_scatter$category)], ann = FALSE)
  legend("top", legend = c("#d99e73", "#de4500", "#a6e6db", "#202d85"), horiz = TRUE, 
         xpd = TRUE, inset = c(-0.24), col = sanzo4("c339"), pch = 15, bty = "n")

  barplot(df_bar$y, col = sanzo4("c341"), main = "Combination 341", 
          ylim = c(0, 20), border = NA)
  plot(df_scatter$value, pch = 18:20, 
       col = sanzo4("c341") [unclass(df_scatter$category)], ann = FALSE)
  legend("top", legend = c("#ff616b", "#328e13", "#172713", "#a6e6db"), horiz = TRUE, 
         xpd = TRUE, inset = c(-0.24), col = sanzo4("c341"), pch = 15, bty = "n")

  barplot(df_bar$y, col = sanzo4("c348"), main = "Combination 348", 
          ylim = c(0, 20), border = NA)
  plot(df_scatter$value, pch = 18:20, 
       col = sanzo4("c348") [unclass(df_scatter$category)], ann = FALSE)
  legend("top", legend = c("#bcd382", "#328e13", "#172713", "#340059"), horiz = TRUE, 
         xpd = TRUE, inset = c(-0.24), col = sanzo4("c348"), pch = 15, bty = "n")

}

# Print demos for all palettes in package.
demo.all <- function() {
  demo2()
  demo3()
  demo4()
}

# Print information associated with duo palettes.
# Hexadecimals
# Color names
# Palette name in Sanzo Wada site
sanzo.info2 <- function() {
  
  long_names <- c("Combination 6", "Combination 7", "Combination 8", "Combination 33", 
                  "Combination 35", "Combination 47", "Combination 70", "Combination 71", 
                  "Combination 74", "Combination 79", "Combination 85", "Combination 91",
                  "Combination 95", "Combination 102", "Combination 103", "Combination 106", 
                  "Combination 114", "Combination 118", "Combination 119", "Combination 229")
  short_names <- c("c006", "c007", "c008", "c033", "c035", "c047", "c070", "c071", "c074", "c079", 
             "c085", "c091", "c095", "c102", "c103", "c106", "c114", "c118", "c119", "c229")
  hex <- c("#ff616b, #000831", "#ff5200, #b3e8c2", "#c2612c, #b8b8ff", "#b85e00, #1b3644",
           "#b08699, #a10b2b", "#c9303e, #bfabcc", "#b85e00, #405416", "#a90636, #d99e73", 
           "#b5ffc2, #2dbc94", "#651300, #2dbc94", "#c74300, #008aa1", "#5c2c45, #c05200",
           "#681916, #06004f", "#ebd999, #c05200", "#c2612c, #2d0060", "#008aa1, #06004f",
           "#ffab00, #008aa1", "#e0b81f, #362304", "#a6e6db, #0d2b52", "#172713, #b5d1cc")
  url <- c("https://sanzo-wada.dmbk.io/combination/6", "https://sanzo-wada.dmbk.io/combination/7",
           "https://sanzo-wada.dmbk.io/combination/8", "https://sanzo-wada.dmbk.io/combination/33",
           "https://sanzo-wada.dmbk.io/combination/35", "https://sanzo-wada.dmbk.io/combination/47",
           "https://sanzo-wada.dmbk.io/combination/70", "https://sanzo-wada.dmbk.io/combination/71",
           "https://sanzo-wada.dmbk.io/combination/74", "https://sanzo-wada.dmbk.io/combination/79",
           "https://sanzo-wada.dmbk.io/combination/85", "https://sanzo-wada.dmbk.io/combination/91",
           "https://sanzo-wada.dmbk.io/combination/95", "https://sanzo-wada.dmbk.io/combination/102",
           "https://sanzo-wada.dmbk.io/combination/103", "https://sanzo-wada.dmbk.io/combination/106",
           "https://sanzo-wada.dmbk.io/combination/114", "https://sanzo-wada.dmbk.io/combination/118",
           "https://sanzo-wada.dmbk.io/combination/119", "https://sanzo-wada.dmbk.io/combination/229")
    
  df <- data.frame(long_names, short_names, hex, url)
  colnames(df) <- c("DUO PALETTE", "ID", "HEX VALUES", "URL")
  return(df)
  
}

# Print information associated with palette.
# Hexadecimals
# Color names
# Palette name in Sanzo Wada site
sanzo.info3 <- function() {
  
  long_names <- c("Combination 121", "Combination 139", "Combination 142", "Combination 148", 
                  "Combination 149", "Combination 157", "Combination 163", "Combination 171", 
                  "Combination 172", "Combination 174", "Combination 194", "Combination 204",
                  "Combination 205", "Combination 207", "Combination 223", "Combination 226", 
                  "Combination 232", "Combination 239", "Combination 240", "Combination 343")
  short_names <- c("c121", "c139", "c142", "c148", "c149", "c157", "c163", "c171", "c172", "c174", 
             "c194", "c204", "c205", "c207", "c223", "c226", "c232", "c239", "c240", "c343")
  hex <- c("#6c2b11, #d99e73, #405416", "#96bfe6, #000831, #b5d1cc", "#9e194d, #baa600, #96bfe6",
           "#d1bd19, #ffab00, #29bdad", "#d1bd19, #ff5200, #0f261f", "#6f0043, #d1bd19, #4f8fe6",
           "#ffe600, #b5ffc2, #008aa1", "#730f1f, #ff8c00, #b3e8c2", "#c2612c, #008aa1, #3400a3",
           "#ffa6d9, #bfabcc, #6b2e63", "#fa2b00, #ffcfc4, #4f8fe6", "#b319ab, #c2612c, #a6e6db",
           "#730f1f, #f59994, #2619d1", "#9b5348, #b3e8c2, #000000", "#b08699, #d99e73, #b5ffc2",
           "#5c2c45, #ffb852, #2619d1", "#d60036, #f2ad78, #000831", "#b08699, #c4bf33, #b3e8c2",
           "#ff788c, #ffff00, #29bdad", "#a93400, #ebd999, #505423") 
  url <- c("https://sanzo-wada.dmbk.io/combination/121", "https://sanzo-wada.dmbk.io/combination/139", 
           "https://sanzo-wada.dmbk.io/combination/142", "https://sanzo-wada.dmbk.io/combination/148",
           "https://sanzo-wada.dmbk.io/combination/149", "https://sanzo-wada.dmbk.io/combination/157",
           "https://sanzo-wada.dmbk.io/combination/163", "https://sanzo-wada.dmbk.io/combination/171",
           "https://sanzo-wada.dmbk.io/combination/172", "https://sanzo-wada.dmbk.io/combination/174",
           "https://sanzo-wada.dmbk.io/combination/194", "https://sanzo-wada.dmbk.io/combination/204",
           "https://sanzo-wada.dmbk.io/combination/205", "https://sanzo-wada.dmbk.io/combination/207",
           "https://sanzo-wada.dmbk.io/combination/223", "https://sanzo-wada.dmbk.io/combination/226",
           "https://sanzo-wada.dmbk.io/combination/232", "https://sanzo-wada.dmbk.io/combination/239",
           "https://sanzo-wada.dmbk.io/combination/240", "https://sanzo-wada.dmbk.io/combination/343")
  
  df <- data.frame(long_names, short_names, hex, url)
  colnames(df) <- c("TRIO PALETTE", "ID", "HEX VALUES", "URL")
  return(df)
  
}

# Print information associated with palette.
# Hexadecimals
# Color names
# Palette name in Sanzo Wada site
sanzo.info4 <- function() {
  
  long_names <- c("Combination 249", "Combination 252", "Combination 263", "Combination 268", 
                  "Combination 271", "Combination 273", "Combination 279", "Combination 283", 
                  "Combination 289", "Combination 293", "Combination 296", "Combination 302",
                  "Combination 310", "Combination 321", "Combination 329", "Combination 330", 
                  "Combination 332", "Combination 339", "Combination 341", "Combination 348")
  short_names <- c("c249", "c252", "c263", "c268", "c271", "c273", "c279", "c283", "c289", "c293", 
             "c296", "c302", "c310", "c321", "c329", "c330", "c332", "c339", "c341", "c348")
  hex <- c("#681916, #c0b490, #d1bd19, #417777", "#e62e73, #b85e00, #baa600, #2dbc94",
           "#a93400, #f2ad78, #b5ffc2, #1b3644", "#b08699, #b85e00, #172713, #bfffe6",
           "#b90078, #94ff94, #2dbc94, #0f261f", "#ffb3f0, #6f0043, #9b5348, #b5d1cc",
           "#b85e00, #f59994, #c0b490, #0d2b52", "#a7374b, #730f1f, #85b857, #6bffb3",
           "#f2ff26, #bdf226, #202d85, #06004f", "#b85e00, #b5ffc2, #65a98f, #40c945",
           "#f5f5b8, #d99e73, #5e4017, #1b3644", "#ffb852, #c0b490, #bfffe6, #008aa1",
           "#f5f5b8, #f2ad78, #718600, #172713", "#b08699, #f5f5b8, #172713, #96bfe6",
           "#ffb852, #bfabcc, #340059, #1b3644", "#bcd382, #bfffe6, #96bfe6, #2dbc94",
           "#ff7399, #d50c42, #172713, #00592e", "#d99e73, #de4500, #a6e6db, #202d85",
           "#ff616b, #328e13, #172713, #a6e6db", "#bcd382, #328e13, #172713, #340059")
  url <- c("https://sanzo-wada.dmbk.io/combination/249", "https://sanzo-wada.dmbk.io/combination/252",
           "https://sanzo-wada.dmbk.io/combination/263", "https://sanzo-wada.dmbk.io/combination/268",
           "https://sanzo-wada.dmbk.io/combination/271", "https://sanzo-wada.dmbk.io/combination/273",
           "https://sanzo-wada.dmbk.io/combination/279", "https://sanzo-wada.dmbk.io/combination/283",
           "https://sanzo-wada.dmbk.io/combination/289", "https://sanzo-wada.dmbk.io/combination/293",
           "https://sanzo-wada.dmbk.io/combination/296", "https://sanzo-wada.dmbk.io/combination/302",
           "https://sanzo-wada.dmbk.io/combination/310", "https://sanzo-wada.dmbk.io/combination/321",
           "https://sanzo-wada.dmbk.io/combination/329", "https://sanzo-wada.dmbk.io/combination/330",
           "https://sanzo-wada.dmbk.io/combination/332", "https://sanzo-wada.dmbk.io/combination/339",
           "https://sanzo-wada.dmbk.io/combination/341", "https://sanzo-wada.dmbk.io/combination/348")
  
  df <- data.frame(long_names, short_names, hex, url)
  colnames(df) <- c("QUAD PALETTE", "ID", "HEX VALUES", "URL")
  return(df)
  
}

# Print information associated with palette.
# Hexadecimals
# Color names
# Palette name in Sanzo Wada site
sanzo.info.all <- function() {
  
  d <- sanzo.info2()
  t <- sanzo.info3()
  q <- sanzo.info4()
  
  df <- merge(d, t, all = TRUE)
  df <- merge(df, q, all = TRUE)
  return(df)
  
}

knitr::kable(sanzo.info2())
knitr::kable(sanzo.info3())
knitr::kable(sanzo.info4())



```

# Demo duos in base R.

```{r demoDuos, echo = FALSE}

demo2()

```

# Demo trios in base R.

```{r demoTrios, echo = FALSE}

demo3()

```

# Demo quads in base R.

```{r demoQuad, echo = FALSE}

demo4()

```

# Demo in ggplot2.

## Scatter plots.

### Combination 205
#### theme_tufte (ggthemes), geom_rug, alpha = 3/4.

```{r gg_scatter1, echo = FALSE, warning = FALSE}

ggplot(raw, aes(CT1, CT2, color = as.factor(Concentration))) + 
  geom_point(aes(shape = Target),
             size = 2, 
             alpha = 3/4) +
  geom_rug() + 
  theme_tufte(ticks = FALSE) + 
  scale_color_manual(name = "PLASMID CONCENTRATION", 
                     values = sanzo3("c205")) + 
  scale_shape_manual(name = "TARGET", 
                     values = c(17, 18, 19)) + 
  theme(axis.text = element_text(size = 8),
        axis.title = element_text(size = 10),
        plot.title = element_text(size = 10, face = "bold", hjust = 0.5),
        legend.title = element_text(size = 10)) +
  labs(y = "REPLICATE 2\n", 
        x = "\nREPLICATE 1", 
        fill = "TARGET", 
        title = "MEAN PLASMID CONTROL Cq VALUE BY qPCR TARGET\n") + 
  geom_smooth(method = lm, 
              se = FALSE, 
              color = "darkslategray", 
              size = 0.5) +
  scale_y_continuous(limits = c(15, 35)) + 
  scale_x_continuous(limits = c(15, 35)) +
  geom_abline(intercept = 0, 
              slope = 1, 
              linetype = "dotted",
              color = "ivory3")

```

### Combination 194
#### theme_tufte (ggthemes), geom_rug, alpha = 3/4.

```{r gg_scatter2, echo = FALSE, warning = FALSE}
ggplot(raw, aes(CT1, CT2, color = as.factor(Concentration))) + 
  geom_point(aes(shape = Target),
             size = 2, 
             alpha = 3/4) +
  geom_rug() + 
  theme_tufte(ticks = FALSE) + 
  scale_color_manual(name = "PLASMID CONCENTRATION", 
                     values = sanzo3("c194")) + 
  scale_shape_manual(name = "TARGET", 
                     values = c(17, 18, 19)) + 
  theme(axis.text = element_text(size = 8),
        axis.title = element_text(size = 10),
        plot.title = element_text(size = 10, face = "bold", hjust = 0.5),
        legend.title = element_text(size = 10)) +
  labs(y = "REPLICATE 2\n", 
        x = "\nREPLICATE 1", 
        fill = "TARGET", 
        title = "MEAN PLASMID CONTROL Cq VALUE BY qPCR TARGET\n") + 
  geom_smooth(method = lm, 
              se = FALSE, 
              color = "darkslategray", 
              size = 0.5) +
  scale_y_continuous(limits = c(15, 35)) + 
  scale_x_continuous(limits = c(15, 35)) +
  geom_abline(intercept = 0, 
              slope = 1, 
              linetype = "dotted",
              color = "ivory3")

```

### Combination 121
#### theme_tufte (ggthemes), geom_rug, alpha = 3/4.

```{r gg_scatter3, echo = FALSE, warning = FALSE}
ggplot(raw, aes(CT1, CT2, color = as.factor(Concentration))) + 
  geom_point(aes(shape = Target),
             size = 2, 
             alpha = 3/4) +
  geom_rug() + 
  theme_tufte(ticks = FALSE) + 
  scale_color_manual(name = "PLASMID CONCENTRATION", 
                     values = sanzo3("c121")) + 
  scale_shape_manual(name = "TARGET", 
                     values = c(17, 18, 19)) + 
  theme(axis.text = element_text(size = 8),
        axis.title = element_text(size = 10),
        plot.title = element_text(size = 10, face = "bold", hjust = 0.5),
        legend.title = element_text(size = 10)) +
  labs(y = "REPLICATE 2\n", 
        x = "\nREPLICATE 1", 
        fill = "TARGET", 
        title = "MEAN PLASMID CONTROL Cq VALUE BY qPCR TARGET\n") + 
  geom_smooth(method = lm, 
              se = FALSE, 
              color = "darkslategray", 
              size = 0.5) +
  scale_y_continuous(limits = c(15, 35)) + 
  scale_x_continuous(limits = c(15, 35)) +
  geom_abline(intercept = 0, 
              slope = 1, 
              linetype = "dotted",
              color = "ivory3")

```

### Combination 207
#### theme_tufte (ggthemes), geom_rug, alpha = 3/4.

```{r gg_scatter4, echo = FALSE, warning = FALSE}

ggplot(raw, aes(CT1, CT2, color = as.factor(Concentration))) + 
  geom_point(aes(shape = Target),
             size = 2, 
             alpha = 3/4) +
  geom_rug() + 
  theme_tufte(ticks = FALSE) + 
  scale_color_manual(name = "PLASMID CONCENTRATION", 
                     values = sanzo3("c207")) + 
  scale_shape_manual(name = "TARGET", 
                     values = c(17, 18, 19)) + 
  theme(axis.text = element_text(size = 8),
        axis.title = element_text(size = 10),
        plot.title = element_text(size = 10, face = "bold", hjust = 0.5),
        legend.title = element_text(size = 10)) +
  labs(y = "REPLICATE 2\n", 
        x = "\nREPLICATE 1", 
        fill = "TARGET", 
        title = "MEAN PLASMID CONTROL Cq VALUE BY qPCR TARGET\n") + 
  geom_smooth(method = lm, 
              se = FALSE, 
              color = "darkslategray", 
              size = 0.5) +
  scale_y_continuous(limits = c(15, 35)) + 
  scale_x_continuous(limits = c(15, 35)) +
  geom_abline(intercept = 0, 
              slope = 1, 
              linetype = "dotted",
              color = "ivory3")

```


### Combination 172
#### theme_tufte (ggpthemes), geom_rug, alpha = 3/4.

```{r gg_scatter5, echo = FALSE, warning = FALSE}

ggplot(raw, aes(CT1, CT2, color = as.factor(Concentration))) + 
  geom_point(aes(shape = Target),
             size = 2, 
             alpha = 3/4) +
  geom_rug() + 
  theme_tufte(ticks = FALSE) + 
  scale_color_manual(name = "PLASMID CONCENTRATION", 
                     values = sanzo3("c172")) + 
  scale_shape_manual(name = "TARGET", 
                     values = c(17, 18, 19)) + 
  theme(axis.text = element_text(size = 8),
        axis.title = element_text(size = 10),
        plot.title = element_text(size = 10, face = "bold", hjust = 0.5),
        legend.title = element_text(size = 10)) +
  labs(y = "REPLICATE 2\n", 
        x = "\nREPLICATE 1", 
        fill = "TARGET", 
        title = "MEAN PLASMID CONTROL Cq VALUE BY qPCR TARGET\n") + 
  geom_smooth(method = lm, 
              se = FALSE, 
              color = "darkslategray", 
              size = 0.5) +
  scale_y_continuous(limits = c(15, 35)) + 
  scale_x_continuous(limits = c(15, 35)) +
  geom_abline(intercept = 0, 
              slope = 1, 
              linetype = "dotted",
              color = "ivory3")

```

## Violin plots.
#### theme_hc (ggthemes), grid-up via cowplot.

```{r violin, echo = FALSE, warning = FALSE}

  x1 <- rnorm(40, mean = 80.2, sd = 4)
  x2 <- rnorm(20, mean = 75.3, sd = 5)
  x3 <- rnorm(30, mean = 63.3, sd = 4)
  x4 <- rnorm(20, mean = 55.8, sd = 3)
  
  y1 <- rnorm(40, mean = 55.8, sd = 3)
  y2 <- rnorm(20, mean = 63.3, sd = 4)
  y3 <- rnorm(30, mean = 55.8, sd = 5)
  y4 <- rnorm(20, mean = 80.2, sd = 4)
  
  x <- c(x1, x2, x3, x4)
  y <- c(y1, y2, y3, y4)
  
  category <- c(1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 
                1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1,
                2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 
                3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3,
                3, 3, 3, 3, 3, 3, 3, 3, 3, 3,
                4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4)
  
  df_scatter <- data.frame(x, y, category)

vio1 <- ggplot(df_scatter, aes(category, x), color = as.factor(category)) + 
  geom_violin(aes(fill = factor(category)), trim = FALSE) + 
  theme_hc() + 
  scale_fill_manual(name = "", 
                     values = sanzo4("c321")) + 
  scale_color_manual(name = "", 
                     values = sanzo4("c321")) + 
  theme(axis.text = element_text(size = 8),
        axis.title = element_text(size = 10),
        plot.title = element_text(size = 10, face = "bold", hjust = 0.5),
        legend.position = "none") +
  labs(y = "", 
        x = "\nCombination 321", 
        fill = "", 
        title = "") +
  theme(aspect.ratio = 1)


vio2 <- ggplot(df_scatter, aes(category, x), color = as.factor(category)) + 
  geom_violin(aes(fill = factor(category)), trim = FALSE) + 
  theme_hc() + 
  scale_fill_manual(name = "", 
                     values = sanzo4("c339")) + 
  scale_color_manual(name = "", 
                     values = sanzo4("c339")) + 
  theme(axis.text = element_text(size = 8),
        axis.title = element_text(size = 10),
        plot.title = element_text(size = 10, face = "bold", hjust = 0.5),
        legend.position = "none") +
  labs(y = "", 
        x = "\nCombination 339", 
        fill = "", 
        title = "") +
  theme(aspect.ratio = 1)


plot_grid(vio1, vio2)

```

## Concatenating two duos for a custom quad.
#### theme_hc (ggthemes), alpha = 5/6.

```{r concat, echo = FALSE, message = FALSE, warning = FALSE}
c033 <- sanzo2("c033")
c095 <- sanzo2("c095")
custom <- c(c033, c095)

ggplot(df_scatter, aes(category, x), color = as.factor(category)) + 
  geom_violin(aes(fill = factor(category)), alpha = 5/6, trim = FALSE) + 
  theme_hc() + 
  scale_fill_manual(name = "", 
                     values = custom) + 
  scale_color_manual(name = "", 
                     values = custom) + 
  theme(axis.text = element_text(size = 8),
        axis.title = element_text(size = 10),
        plot.title = element_text(size = 10, face = "bold", hjust = 0.5),
        legend.position = "none") +
  labs(y = "", 
        x = "\nCombination 033 + Combination 095", 
        fill = "", 
        title = "") +
  theme(aspect.ratio = 1)

```

## Gradient.
#### Continuous colors via scale_fill_gradientn(), theme_few (ggthemes).

```{r gradient, echo = FALSE, warning = FALSE}

grad1 <- ggplot(faithfuld, aes(waiting, eruptions)) +
  geom_raster(aes(fill = density), interpolate = TRUE) +
  theme_few() +
  scale_fill_gradientn(colors = sanzo2("c114")) +
  labs(y = "", 
        x = "", 
        fill = "", 
        title = "Combination 114\n")

grad2 <- ggplot(faithfuld, aes(waiting, eruptions)) +
  geom_raster(aes(fill = density), interpolate = TRUE) +
  theme_few() +
  scale_fill_gradientn(colors = sanzo3("c163")) +
  labs( y= "", 
        x = "", 
        fill = "", 
        title = "Combination 163\n")

grad3 <- ggplot(faithfuld, aes(waiting, eruptions)) +
  geom_raster(aes(fill = density), interpolate = TRUE) +
  theme_few() +
  scale_fill_gradientn(colors = sanzo3("c171")) +
  labs(y = "", 
        x = "", 
        fill = "", 
        title = "Combination 171\n")

grad4 <- ggplot(faithfuld, aes(waiting, eruptions)) +
  geom_raster(aes(fill = density), interpolate = TRUE) +
  theme_few() +
  scale_fill_gradientn(colors = sanzo2("c102")) +
  labs(y = "", 
        x = "", 
        fill = "", 
        title = "Combination 102\n")

plot_grid(grad1, grad2, grad3, grad4)

```

## Bar plots.

#### theme_tufte (ggthemes).

```{r gg_bar1, echo = FALSE, warning = FALSE}

bar1 <- ggplot(mean, aes(fill = Concentration, y = CT, x = Target)) + 
  geom_bar(position = "dodge", stat = "identity") +
  theme_tufte() +
  scale_fill_manual(values = sanzo3("c343")) +
  theme(axis.text = element_text(size = 8),
        axis.title = element_text(size = 10),
        plot.title = element_text(size = 10, face = "bold", hjust = 0.5),
        legend.title = element_text(size = 10),
        legend.position = "right",
        legend.direction = "vertical") +
  labs(y = "", 
        x = "", 
        fill = "", 
        title = "")


bar2 <- ggplot(mean, aes(fill = Concentration, y = CT, x = Target)) + 
  geom_bar(position = "dodge", stat = "identity") +
  theme_tufte() +
  scale_fill_manual(values = sanzo4("c252")) +
  theme(axis.text = element_text(size = 8),
        axis.title = element_text(size = 10),
        plot.title = element_text(size = 10, face = "bold", hjust = 0.5),
        legend.title = element_text(size = 10),
        legend.position = "right",
        legend.direction = "vertical") +
  labs(y = "", 
        x = "", 
        fill = "", 
        title = "")


bar3 <- ggplot(mean, aes(fill = Concentration, y = CT, x = Target)) + 
  geom_bar(position = "dodge", stat = "identity") +
  theme_tufte() +
  scale_fill_manual(values = sanzo4("c279")) +
  theme(axis.text = element_text(size = 8),
        axis.title = element_text(size = 10),
        plot.title = element_text(size = 10, face = "bold", hjust = 0.5),
        legend.title = element_text(size = 10),
        legend.position = "right",
        legend.direction = "vertical") +
  labs(y = "", 
        x = "", 
        fill = "", 
        title = "")


bar4 <- ggplot(mean, aes(fill = Concentration, y = CT, x = Target)) + 
  geom_bar(position = "dodge", stat = "identity") +
  theme_tufte() +
  scale_fill_manual(values = sanzo4("c310")) +
  theme(axis.text = element_text(size = 8),
        axis.title = element_text(size = 10),
        plot.title = element_text(size = 10, face = "bold", hjust = 0.5),
        legend.title = element_text(size = 10),
        legend.position = "right",
        legend.direction = "vertical") +
  labs(y = "", 
        x = "", 
        fill = "", 
        title = "")

plot_grid(bar1, bar2, bar3, bar4, labels = c("Combination 343", "Combination 252", "Combination 279", "Combination 310"), label_size = 12)

```

#### theme_few (ggthemes).

```{r gg_bar2, echo = FALSE, warning = FALSE}

bar1 <- ggplot(mean, aes(fill = Concentration, y = CT, x = Target)) + 
  geom_bar(stat = "identity") +
  theme_few() +
  scale_fill_manual(values = sanzo4("c296"), labels = c("A", "B", "C")) + 
  theme(axis.text = element_text(size = 8),
        axis.title = element_text(size = 10),
        plot.title = element_text(size = 10, face = "bold", hjust = 0.5),
        legend.title = element_text(size = 10),
        legend.position = "right",
        legend.direction = "vertical") +
  scale_x_discrete(labels = c("1", "2", "3")) +
  labs(y = "", 
        x = "", 
        fill = "", 
        title = "")


bar2 <- ggplot(mean, aes(fill = Concentration, y = CT, x = Target)) + 
  geom_bar(stat = "identity") +
  theme_few() +
  scale_fill_manual(values = sanzo3("c157"), labels = c("A", "B", "C")) + 
  theme(axis.text = element_text(size = 8),
        axis.title = element_text(size = 10),
        plot.title = element_text(size = 10, face = "bold", hjust = 0.5),
        legend.title = element_text(size = 10),
        legend.position = "right",
        legend.direction = "vertical") +
  scale_x_discrete(labels = c("1", "2", "3")) +
  labs(y = "", 
        x = "", 
        fill = "", 
        title = "")



bar3 <- ggplot(mean, aes(fill = Concentration, y = CT, x = Target)) + 
  geom_bar(stat = "identity") +
  theme_few() +
  scale_fill_manual(values = sanzo4("c249"), labels = c("A", "B", "C")) + 
  theme(axis.text = element_text(size = 8),
        axis.title = element_text(size = 10),
        plot.title = element_text(size = 10, face = "bold", hjust = 0.5),
        legend.title = element_text(size = 10),
        legend.position = "right",
        legend.direction = "vertical") +
  scale_x_discrete(labels = c("1", "2", "3")) +
  labs(y = "", 
        x = "", 
        fill = "", 
        title = "")


bar4 <- ggplot(mean, aes(fill = Concentration, y = CT, x = Target)) + 
  geom_bar(stat = "identity") +
  theme_few() +
  scale_fill_manual(values = sanzo4("c268"), labels = c("A", "B", "C")) + 
  theme(axis.text = element_text(size = 8),
        axis.title = element_text(size = 10),
        plot.title = element_text(size = 10, face = "bold", hjust = 0.5),
        legend.title = element_text(size = 10),
        legend.position = "right",
        legend.direction = "vertical") +
  scale_x_discrete(labels = c("1", "2", "3")) +
  labs(y = "", 
        x = "", 
        fill = "", 
        title = "")

plot_grid(bar1, bar2, bar3, bar4, labels = c("Combination 296", "Combination 157", "Combination 249", "Combination 268"), label_size = 12)

```
