---
title: "Vignette"
author: "Jacqueline R.M.A. Maasch"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{sanzo_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


# ```sanzo```: Color Palettes Based on the Works of Sanzo Wada

An R package by JRMA Maasch (2019).

This vignette is intended to share function documentation and code for several different use cases for this package. Find more information about this package at: https://github.com/jmaasch/sanzo

```{r hide, include = FALSE}

# Load packages for ggplot2 demos.
library(ggplot2)
library(ggthemes)

data("iris")

# Read in data for ggplot2 demos.
raw <- read.csv("/Users/razel/Desktop/PROGS/R_practice/2019/sth_plasmid_ct_mean_raw.csv")
mean <- read.csv("/Users/razel/Desktop/PROGS/R_practice/2019/sth_plasmid_ct_mean.csv")

```

## Installation.

```{r setup}
# Install package if needed.
# devtools::install_github("jmaasch/sanzo")

# Load.
library(sanzo)
```

## Functions.
* ```sanzo.duo(palette_name)``` : return duo palette
* ```sanzo.trio(palette_name)``` : return trio palette
* ```sanzo.quad(palette_name)``` : return quad palette
* ```sanzo.demo2()``` : print demo plots for all duo palettes
* ```sanzo.demo3()``` : print demo plots for all trio palettes
* ```sanzo.demo4()``` : print demo plots for all quad palettes
* ```sanzo.demo.all()``` : print demo plots for all palettes
* ```sanzo.info2()``` : return data frame of hexadecimals and urls for all duo palettes
* ```sanzo.info3()``` : return data frame of hexadecimals and urls for all trio palettes
* ```sanzo.info4()``` : return data frame of hexadecimals and urls for all quad palettes
* ```sanzo.info.all()``` : return data frame of hexadecimals and urls for all palettes

## View function documentation.

Precede any function by a question mark to access description, arguments, return value, and usage suggestions.

```{r doc}

# Examples:
?sanzo.info2()
?sanzo.trio()

```

## View metadata for all duos, trios, and quads.

The following functions return a data frame containing long-form names, short-form IDs, hexadecimal values, and links to Dain M. Blodorn Kim's https://sanzo-wada.dmbk.io for further palette information.

```{r info}

knitr::kable(sanzo.info2())
knitr::kable(sanzo.info3())
knitr::kable(sanzo.info4())

```


## View palette demos.

To illustrate their potential, each color combination can be demo'd via base R scatter and bar plots. The output of ```sanzo.demo2()```, ```sanzo.demo3()```, ```sanzo.demo4()```, and ```sanzo.demo.all()``` can be previewed at https://github.com/jmaasch/sanzo.

## Use with base R.

These examples use data from the ```datasets``` package and should be replicable.

### Scatter plot.

```{r base}

plot(iris$Sepal.Width, iris$Petal.Width, pch = 18:20, main = "Combination 121",
     ylab = "", xlab = "", col = sanzo.trio("c121") [unclass(iris$Species)])

```

### Bar plot.

```{r base2}
barplot(BOD$demand, col = sanzo.trio("c139"), main = "Combination 139", 
        ylim = c(0, 20), border = NA)
```

## Use with ```ggplot2``` and the ```ggthemes``` extension.

### Violin plot.

```{r violin_data, echo = FALSE}
  x1 <- rnorm(40, mean = 80.2, sd = 4)
  x2 <- rnorm(20, mean = 75.3, sd = 5)
  x3 <- rnorm(30, mean = 63.3, sd = 4)
  x4 <- rnorm(20, mean = 55.8, sd = 3)
  
  y1 <- rnorm(40, mean = 55.8, sd = 3)
  y2 <- rnorm(20, mean = 63.3, sd = 4)
  y3 <- rnorm(30, mean = 55.8, sd = 5)
  y4 <- rnorm(20, mean = 80.2, sd = 4)
  
  x <- c(x1, x2, x3, x4)
  y <- c(y1, y2, y3, y4)
  
  category <- c(1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 
                1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1,
                2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 
                3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3,
                3, 3, 3, 3, 3, 3, 3, 3, 3, 3,
                4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4)
  
  df_scatter <- data.frame(x, y, category)

```

```{r violin, warning = FALSE}

ggplot(df_scatter, aes(category, x), color = as.factor(category)) + 
  geom_violin(aes(fill = factor(category)), trim = FALSE) + 
  theme_hc() + 
  scale_fill_manual(name = "", 
                     values = sanzo.quad("c279")) + 
  theme(axis.text = element_text(size = 8),
        axis.title = element_text(size = 10),
        plot.title = element_text(size = 10, face = "bold", hjust = 0.5),
        legend.position = "none") +
  labs(y = "", 
        x = "", 
        fill = "", 
        title = "Combination 279\n") +
  theme(aspect.ratio = 1)
```

### Use as gradient.

By default, ```sanzo``` palettes are discrete. There are multiple ways to achieve a gradient. For example, using ```scale_fill_gradientn``` or ```scale_color_gradientn``` in ```ggplot2``` allows you to use any ```sanzo``` palette as a continuous gradient.

This example uses data from the ```datasets``` package and should be replicable. Continuous colors via ```scale_fill_gradientn``` and plot theme via ```theme_few``` from the ```ggthemes``` extension.

```{r gradient, warning = FALSE}

ggplot(faithfuld, aes(waiting, eruptions)) +
  geom_raster(aes(fill = density), interpolate = TRUE) +
  theme_few() +
  scale_fill_gradientn(colors = sanzo.trio("c226")) +
  labs(y = "", 
        x = "", 
        fill = "", 
        title = "Combination 226\n")

```

### Bar plot.

```{r stacked_bar, warning = FALSE}

ggplot(mean, aes(fill = Concentration, y = CT, x = Target)) + 
  geom_bar(stat = "identity") +
  theme_few() +
  scale_fill_manual(values = sanzo.trio("c239"), labels = c("A", "B", "C")) + 
  theme(axis.text = element_text(size = 8),
        axis.title = element_text(size = 10),
        plot.title = element_text(size = 10, face = "bold", hjust = 0.5),
        legend.title = element_text(size = 10),
        legend.position = "bottom",
        legend.direction = "horizontal") +
  scale_x_discrete(labels = c("1", "2", "3")) +
  labs(y = "", 
        x = "", 
        fill = "", 
        title = "Combination 239")

```
