---
title: "Vignette"
author: "Jacqueline R.M.A. Maasch"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{sanzo_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


# ```sanzo```: Color Palettes Based on the Works of Sanzo Wada

An R package by JRMA Maasch (2019).

This vignette is intended to share function documentation and code for several different use cases Find further information and suggested uses at https://github.com/jmaasch/sanzo.

## Load package

```{r install, warning = FALSE, error = FALSE, eval = FALSE}

# Install development version of package, if needed.
devtools::install_github("jmaasch/sanzo")

```

```{r load, warning = FALSE, error = FALSE}

# Load package.
library(sanzo)

```

## Functions.
* ```sanzo.duo(palette_name)``` : return duo palette
* ```sanzo.trio(palette_name)``` : return trio palette
* ```sanzo.quad(palette_name)``` : return quad palette
* ```sanzo.demo2()``` : print demo plots for all duo palettes
* ```sanzo.demo3()``` : print demo plots for all trio palettes
* ```sanzo.demo4()``` : print demo plots for all quad palettes
* ```sanzo.demo.all()``` : print demo plots for all palettes
* ```sanzo.info2()``` : return data frame of hexadecimals and urls for all duo palettes
* ```sanzo.info3()``` : return data frame of hexadecimals and urls for all trio palettes
* ```sanzo.info4()``` : return data frame of hexadecimals and urls for all quad palettes
* ```sanzo.info.all()``` : return data frame of hexadecimals and urls for all palettes

## View function documentation.

Precede any function by a question mark to access description, arguments, return value, and usage suggestions.

```{r doc}

# Examples:
?sanzo.info2()
?sanzo.trio()

```

## View metadata for all duos, trios, and quads.

To quickly access palette names:

```{r names}

names(duos)
names(trios)
names(quads)

```

The following functions return a data frame containing long-form names, short-form IDs, hexadecimal values, and links to Dain M. Blodorn Kim's https://sanzo-wada.dmbk.io for further palette information.

```{r info}

knitr::kable(sanzo.info2())
knitr::kable(sanzo.info3())
knitr::kable(sanzo.info4())

```


## View palette demos.

To illustrate their potential, each color combination can be demo'd via base R scatter and bar plots. 

For easier viewing, try gridding up (**NOTE** -- this will alter ```par``` settings):

```{r grid, eval = FALSE}

# Set up gridded layout, if desired:
graphics::layout(matrix(1:4, nrow = 2))
graphics::par(mar = c(2, 2, 2, 2))

# Print demo plots for duos.
sanzo.demo2()

# Print demo plots for trios.
sanzo.demo3()

# Print demo plots for quads.
sanzo.demo4()

# Print demo plots for all palettes.
sanzo.demo.all()

```

The output of ```sanzo.demo2()```, ```sanzo.demo3()```, ```sanzo.demo4()```, and ```sanzo.demo.all()``` can be previewed at https://github.com/jmaasch/sanzo.

## Use with ```ggplot2```.

View examples of use with ```ggplot2``` at https://github.com/jmaasch/sanzo.

## Use with base R.

These examples use data from the ```datasets``` package and should be replicable.

### Scatter plot.

```{r base}

graphics::plot(iris$Sepal.Width, iris$Petal.Width, pch = 18:20,
               main = "Combination 121", ylab = "", xlab = "", 
               col = sanzo.trio("c121") [unclass(iris$Species)])

```

### Bar plot.

```{r base2}

graphics::barplot(BOD$demand, col = sanzo.trio("c239"), 
                  main = "Combination 239", ylim = c(0, 20), border = NA)

```
